A meta-analysis of mental rotation ability in the first years of life

### 2022-04-22 code/analysis.Rmd
Normalize all the line endings

```{r, compute_meta, echo=TRUE}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_ml)
# forest(res_ml)

@@

# Meta-regression with gender
res_gender <- rma.mv(
  gi, vi,
  mods = ~ gender - 1,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_gender)
# forest(res_gender)

@@

```{r, prior_sens, eval=FALSE}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```

# Methods

>>>>

```{r, compute_meta, echo=TRUE}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)

print(res_ml)
# forest(res_ml)

@@

# Meta-regression with gender
res_gender <- rma.mv(
  gi, vi,
  mods = ~ gender - 1,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_gender)

# forest(res_gender)

@@

```{r, prior_sens, eval=FALSE}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)

```

```{r,  echo=TRUE}
library(bootstrap)

theta <- function(x, dat_r) {
  rma.mv(
    yi, vi,
    mods = ~age_months,
    random = ~ group | id,
    data = dat_r[x, ],
    slab = experiment_ids[x]
  )
}

res_jk <- jackknife(1:nrow(dat_r), theta, dat_r)
```
# Methods
